---
title: "Course Project_Practical Machine Learning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
The goal of this project is to predict the manner in which 6 participants performed some exercise as described below. . This is the "classe" variable in the training set. You may use any of the other variables to predict with. The machine learning algorithm described here is applied to the 20 test cases available in the test data.

## Background

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

## Data
Data

The training data for this project are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv

The data for this project come from this source: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har. If you use the document you create for this class for any purpose please cite them as they have been very generous in allowing their data to be used for this kind of assignment.

# List of R libraries for Analysis.



```{r }
rm(list=ls())                
library(knitr)
library(caret)
library(rpart)
library(rpart.plot)
library(rattle)
library(randomForest)
library(corrplot)
library(e1071)
set.seed(12345)
```

## Loading the data and Cleaning Data


```{r}
trainUrl <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testUrl <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"


# Load the dataset into memory
trainingData <- read.csv(url(trainUrl), na.strings = c("NA", "#DIV/0!", ""))
testingData <- read.csv(url(testUrl), na.strings = c("NA", "#DIV/0!", ""))

#
trainingData <- trainingData[, colSums(is.na(trainingData)) == 0]
testingData <- testingData[, colSums(is.na(testingData)) == 0]

# Delete variables that are not related 
trainingData <- trainingData[, -c(1:7)]
testingData <- testingData[, -c(1:7)]

# partioning the training set into two different dataset

traningPartitionData <- createDataPartition(trainingData$classe,  p = 0.7, list = F)
trainingDataSet <- trainingData[traningPartitionData, ]
testingDataSet <- trainingData[-traningPartitionData, ]
dim(trainingData); dim(testingDataSet)

```
## Prediction Model

```{r}
decisionTreeModel <- rpart(classe ~ ., data = trainingDataSet, method = "class")
decisionTreePrediction <- predict(decisionTreeModel, testingDataSet, type = "class")

# Plot Decision Map
rpart.plot(decisionTreeModel, main = "Decision Map", under = T, faclen = 0)


```
### Prediction Model 2: Random Forest

```{r}
randomForestModel <- randomForest(classe ~. , data = trainingDataSet, method = "class")
randomForestPrediction <- predict(randomForestModel, testingDataSet, type = "class")

confusionMatrix(randomForestPrediction, testingDataSet$classe)
```



```{r}
predictionFinal <- predict(randomForestModel, testingDataSet, type = "class")
```

From the result, it show Random Forest accuracy is higher than Decision tree which is 0.9915 > 0.6644. Therefore, we will use random forest to answer the assignment.



